### 2017-06-01 qualification/5-proposal/chapter5.tex
final version of qualification text

This work proposes that it is possible to adapt a malicious node identification scheme originally designed for static networks to a dynamic environment, such as a VANET.
In order to make this possible, it is necessary to identify features in VANETs that show that nodes can share a long-term relationship, as is the case for social networks.
The arguments for such features are presented in \autoref{section:socialvanets}, while the movement model that enables the simulation of the features is explained in \autoref{section:workingday}.
Through these long-term relationships, it then becomes feasible for nodes to store trust data and share it with other nodes.

By combining a node's own opinions about familiar nodes and trust information received from its neighbors, it is possible to create a model of the surrounding network.
This model includes a trust graph, showing the trust relationships between pair of nodes, which can then be used as input for a malicious node detection algorithm.

@@

In this chapter, the details for the process above are presented.
First, it is shown how vehicles can form long-term relationships and trust one another in a similar way to social networks.
Then, the Working Day Movement Model is presented, along with the reasons why it is best fitted for this work.
Next, a previously existing trust model for complex networks is described, including its advantages and reasons why it could be well-fitted for a vehicular environment, followed by a list of changes that must be made to the model in order for it to handle dynamic networks.
Finally, a schedule for the next steps of the project is shown.

\section{Social Networks and VANETs}
\label{section:socialvanets}
Several of the aforementioned articles state that vehicular networks are, by definition, ephemeral.
That is, the likelihood of two nodes meeting each other twice is too low to be relevant.
In this work, it is argued that such claims are not entirely true.
It stands to reason that, throughout the course of several days, many drivers will take similar routes at similar times of day (e.g. to commute to work) and, therefore, their vehicles will be in similar locations each day.
Additionally, many cities rely on main roads to serve as backbones to their traffic, meaning there is a high density of vehicles on those roads during rush hours.
Since that is true for a notable percentage of a city's fleet, it can also be assumed that those vehicles may frequently encounter each other during their commute.
While two vehicles that share a commute route may not be direct neighbors every day, they will likely be relatively close to each other, meaning few hops separate them in the ad-hoc network.
Furthermore, certain pairs of vehicles are bound to be within communication range of each other nearly every day.
Examples of these include vehicles whose owners are drivers or coworkers.
Such vehicles' trust relationship should become steady over time and, in the case of positive trust, they can use each other's information to learn more about other nodes in the network.

@@

Most cities also have one or more types of mass transit systems (buses or trains).
Those vehicles can also be part of a VANET and communicate with private cars.
Buses share the same roads as cars, but instead of having specific destinations, they travel a predefined route during the whole day, usually tied to a tight schedule.
Trains travel on rails, so their contact with cars is less frequent, but it can also happen on railroad crossings; they travel long distances in relatively short amount of time, which helps the dissemination of data in a VANET.
In the same way that cars have a high probability of meeting more than once during their commutes, it is also very likely that they will meet the same buses and/or trains frequently.

In \cite{da2013effective}, \cite{cunha2014vehicular}, and \cite{cunha2014possible}, the authors attempt to find features usually attributed to social networks in vehicular networks.
By using a data set from Zurich, they show that some metrics, such as clustering coefficient and number of encounters, have peaks during the rush hours.

@@

While certification of identity is an issue in vehicular network, this work will not address it.
There are studies focusing on node identification in VANETs (that is, making sure a node is who it claims to be), in particular through the use of a Public Key Infrastructure (PKI) \cite{wasef2010complementing} 
\cite{kumar2015intelligent}.
One study proposes that such identities must be refreshed with a certain frequency to maintain the privacy of each node \cite{golle2004detecting}.
Although it is important that nodes are not able to lie about identity and are able to maintain their privacy, nodes having valid identities that are persistent over time, so that nodes can identify each other over a long period, is a prerequisite for the model proposed here.

@@

To make use of the above properties, it is important to choose a mobility pattern that properly represents the way vehicles move on a daily basis in the real world.
Therefore, the Working Day Movement Model \cite{ekman2008working} (WDM) will be used.
The model, developed for used in Delay-Tolerant Network (DTN) simulations, includes many of the features that will be necessary to simulate the daily movement of a vehicular network.

As the name implies, the Working Day model abstracts people's movement from their homes to their offices and back.
Each node has a home and a workplace and they need to travel back and forth between those locations on a daily basis.
Occasionally, nodes can also go to other locations for leisure.
Most VANET trust models use the Random Waypoint mobility model, i.e. each node has an origin point, chooses a random location, gets to that location, then chooses another random location and goes there, and so forth.
While this model is efficient for testing trust protocols, it doesn't truly represent vehicle mobility in the real world.
As mentioned above, many drivers have routes they travel on daily, so the Working Day model is a more accurate representation, although it represents the mobility of humans instead of vehicle and requires some adjustments, which will be listed later in this section.

The model proposed by the authors makes use of several other models for specific tasks.
The main mobility model defines nodes and gives them their destinations.
Within it, five other models are used:
\begin{enumerate}
\item 
The \textbf{home activity submodel} describes what nodes do at night, within their homes.
No movement is modeled.
Nodes can be relatives or neighbors, and therefore share the same home.
\item 
The \textbf{office activity submodel} describes the nodes' routines within their offices.
Nodes can go to other locations within the office (such as meeting rooms) and such movement is modeled.
Nodes with share the same office are coworkers.
\item 
The \textbf{evening activity submodel} is responsible for mobility outside the nodes' standard routine. 
They can meet at certain locations (such as restaurants) and spend a few hours gathered with friends.
\item
The \textbf{transport submodel} shows how nodes move around the city.
It includes another tier of submodels, responsible for modeling three different types of transportation: walking, driving, and riding a bus.
Nodes which own a car always use it, while the others can decide to walk or ride a bus depending on the distance between the origin and destination and the available bus stops.
The walking and driving submodels represent similar types of movement, although at different speeds, while the bus submodel follows cyclical routes and can take or deliver passengers at bus stops.
\item
The \textbf{map} represents the city in which the simulation runs.
Its streets constrain the movement of nodes and all homes and offices must be within the map boundaries.
The map can be divided into districts, which increases what the authors define as \textit{locality}.
In the simulation parameters, the number of nodes which reside and work within the same district can be chosen, which means those nodes will rarely leave the district.
Nodes which reside and work in different districts serve to connect the network with their commutes.
\end{enumerate}

By thinking of these submodels for vehicles instead of people, it can become apparent how the frequency and length of encounters between nodes are similar in both instances.
If two vehicles belong to family members or neighbors, they will likely spend most of the night within communication distance, while coworkers' cars spend the office hours close by.
Cars can also meet each other frequently if their drivers go out with friends.
In the vehicular case, there is the added layer of encounters: cars can communicate frequently with buses and other cars that take the same route daily, although the drivers are likely complete strangers.

In the original article, nodes are devices (such as smartphones) being carried by humans.
Therefore, the Working Day model represents not only people's movements inside their cars, but also within their offices, walking on foot, or riding a bus.
To adapt it to a VANET environment, changes need to be made to their definition of node, since they now represent vehicles instead of people. Some of those changes are as follows:
\begin{enumerate}
\item
The office activity submodel no longer needs to model movement within the office and can be identical to the home submodel.
In both, a node can move a small amount once after reaching the office or home, to simulate parking.
This can be done using the Working Day model's parameters.
\item
The walking submodel needs to be disabled, since all nodes will be either cars or buses.
\item
The bus submodel needs to be changed so that each bus is one node in the network, which follows a predefined route with bus stops.
In the original model, each bus could carry several nodes, but this is no longer necessary.
\end{enumerate}
Other necessary changes might become apparent during the development of the study.

@@

The input graph $G = (V,E)$ is a static, connected, and directed graph containing all trust relationships in the network.
Such relationships are binary, so there are no varying degrees of trust: either one node trusts another completely (edge value is $1$), or it distrusts the other completely (edge value is $0$).
The relationships are also directed, meaning that if the value of $A\rightarrow B$ is $1$, $B\rightarrow A$ is not necessarily $1$.

The process for identifying malicious nodes within $G$ is as follows:

First, $G$ is separated into strongly components using Tarjan's algorithm \cite{tarjan1972depth}.
In each of these components, all nodes are connected by edges of value $1$.
In other words, within a single component, all nodes trust one another completely; nodes connected by edges of value $0$ are separated into different components.
Each of these components becomes a node of a component graph $T = (V', E')$.

The creation of the graph $T$ simplifies the remaining computation.
Since each node of $T$ is a vertex $v' \in V'$ and each vertex $v'$ is a component of $G$ in which all nodes trust each other, for the purposes of identifying malicious nodes, all nodes within each of those components can be treated as one.
They can either be benign nodes which legitimately trust one another, or malicious nodes colluding with each other.
After the formation of $T$, one or two heuristics can be used to classify the nodes as benign or malicious.

The \textit{coloring heuristic} uses a graph coloring algorithm, either DSATUR \cite{brelaz1979new} or the algorithm proposed in \cite{mittal2011graph}.
Graph coloring is a classic problem of graph theory, in which the objective is to assign each node in a graph a color so that no two neighboring nodes share the same color.
After running either algorithms with graph $T$, the color with the most nodes in $T$ is classified as correct, and all others are classified as malicious.
Once this information in $T$ is brought back to graph $G$, it is trivial to label the nodes in $G$ as either benign or malicious based on their components' classifications.

The other alternative is the \textit{articulation heuristic}.
It uses a graph articulation algorithm, which does a depth-first search and classifies nodes based on their roles in the spanning tree.
A node $n \in V$ is an articulation if its removal from $G$ makes $G$ a disconnected graph or, in other words, increases the number of connected components of $G$.
Once articulation nodes are found, the heuristic classifies each node as correct if it does not have neighbors that are also articulations.

In the experiments shown in the article, the coloring heuristic shows promising results, identifying a high ratio of the malicious nodes in the network.
The coloring and articulation heuristics can be combined, although the experiments using this combination display a high number of false positives.
Therefore, for the purposes of this paper, only the coloring heuristic will be considered.

\section{Necessary changes to the malicious node identification scheme}
\label{section:changes}
While the algorithm described above works well for static graphs, some important modifications will have to be made to accommodate dynamic graphs.
The main changes planned are described below.

\subsection{Trust graph}
The original work's scope does not include the generation of the trust graph, as it is a parameter to the algorithm.
In dynamic graphs, trust relationships change over time, so how those changes affect our trust model have to be considered.
This includes not only the full figure of the graph, but also each node's views on its neighbors.

\subsection{Strongly connected components}
Strongly connected components, or components in which all nodes have positive trust relationships with each other, are somewhat different in dynamic graphs.
As nodes enter, leave, or change locations in the network, the components will change accordingly.
Therefore, our algorithm will have to work using ``snapshots'' of the graph, meaning each measurement will be valid for a specific timestamp.
In a later step, it might be useful to consider how specific nodes may change over several snapshots.

Since the graph changes with time, for every timestamp $t$, there is a corresponding graph $G_t=(V_t, E_t)$, which includes the available vertices and edges in that moment in time.

\subsection{Graph knowledge}
In the original paper, the malicious nodes are identified by a central entity with access to all nodes' trust values.
Not only does our work plan to decentralize this procedure, having complete knowledge of the graph is unfeasible in large-scale dynamic networks such as VANETs.
Therefore, our algorithm needs to work using only a partial understanding of the network.
For this to be viable, each node will likely have to gather information not only from its views on its neighbors, but also from its neighbor's views and so forth.

@@

Thus, each node will have its own model of the network, and will generate a trust graph $G_i=(V_i, E_i)$, in which $i$ is the node's identifier.
Combined with the necessity of timestamps explained above, this will result in a graph $G_{it}=(V_{it}, E_{it})$ for each node and each timestamp, which will be the input of the new algorithm.
Accordingly, there are also component graphs $T_{it}=(V'_{it}, E'_{it})$, generated on each instance of the algorithm.

@@

Since nodes will interact with each other occasionally and might learn information from other nodes, a range such as $[0,1]$ is useful to express how one trust value can change over time.
As one node learns more about another, the value can grow or diminish and, once it goes above or below a certain threshold, the neighboring node can be deemed trustworthy or not.
The rate in which trust increases or decreases must be experimented with; it could be useful to have trust decrease faster than it increases, but that might also cause false positives in the case of occasional mistakes.

\subsection{Datasets}
The datasets used for experimentation must be changed accordingly.
Instead of using data gathered from social networks, which are static, dynamic network datasets will need to be used, such as traffic information for cities.

At first, the objective is to test using the Working Day Movement Model, setting parameters that contribute to the validation of the algorithm.
When the simulation begins, a set number of nodes will be malicious and, therefore, other nodes will have low trust in them after interacting.
In time, benign and malicious nodes can change their behavior and, accordingly, their trustworthiness will be updated.

@@

\begin{enumerate}
	\item \textbf{Changes to the malicious node identification algorithm}. Develop and adapt the algorithm using the changes listed in \autoref{section:changes}.
	\item \textbf{Changes to the movement model}. Develop and adapt the Working Day Movement Model according to \autoref{section:workingday}.
	\item \textbf{Study and selection of a simulator}. Several simulators for vehicular networks exist, and one must be chosen in order to run simulations using the newly developed model. The Working Day Movement Model was tested with the ONE Simulator \cite{keranen2009one}. The source code for both the simulator and the WDM generation can be found online \cite{onerepo}, and will likely be used for the necessary simulations. 
	\item \textbf{Simulations and adjustments}. Once the core of the project has been developed and a simulation has been chosen, simulations begin. The models may be tweaked in order to achieve better results, and all data from the process will be collected.
	\item \textbf{Analysis of data and results}. With the data collected from simulations, it will be possible to observe the outcome of the proposed trust model. If tweaks were made to the model during simulations, those changes can be listed, showing which ones provided better results.
	\item \textbf{Writing and submission of article}. Having concluded development, an article will be written explaining the motivations, challenges and results of the study. This article will be submitted to a congress.
	\item \textbf{Writing of dissertation}. Finally, the whole process will be detailed within the dissertation.
\end{enumerate}

@@

\begin{table}[h!]
\centering
\begin{tabular}{ |p{0.7cm}||p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}| }
 \hline
 \textbf{Task} & Apr & May & Jun & Jul & Aug & Sep & Oct & Nov & Dec & Jan & Feb & Mar\\
 \hline
 \hline
 \textbf{1} & \checkmark & \checkmark & \checkmark & & & & & & & & &\\
 \hline
 \textbf{2} & & & \checkmark & \checkmark & \checkmark & & & & & & &\\
 \hline
 \textbf{3} & \checkmark & \checkmark & \checkmark & \checkmark & & & & & & & &\\
 \hline
 \textbf{4} & & & & & \checkmark & \checkmark & & & & & &\\
 \hline
 \textbf{5} & & & & & \checkmark & \checkmark & & & & & &\\
 \hline
 \textbf{6} &  &  & & & & \checkmark & \checkmark & \checkmark & & & &\\
 \hline
 \textbf{7} &  &  & & & & & & \checkmark & \checkmark & \checkmark & \checkmark & \checkmark \\
 \hline
\end{tabular}
\caption{Expected schedule}
\label{table:schedule}
\end{table}

>>>>

This work proposes that it is possible to adapt a trust management scheme originally designed for static networks to a dynamic environment, such as a VANET.
In order to make this possible, it is necessary to identify features in VANETs that show that nodes can share a long-term relationship, as is the case for social networks.
%The arguments for such features are presented in \autoref{section:socialvanets}, while the movement model that enables the simulation of the features is explained in \autoref{section:workingday}.
Through these long-term relationships, it then becomes feasible for nodes to store trust data and share it with other nodes.
By combining a node's own opinions about familiar nodes and trust information received from its neighbors, it is possible to create a model of the surrounding network.
This model includes a trust graph, showing the trust relationships between pair of nodes, which can then be used as input for a malicious node detection algorithm.

@@

In this chapter, the details for the above process are presented.
First, it is shown how vehicles can form long-term relationships and trust one another in a similar way to social networks.
Then, the Working Day Movement Model is introduced, along with the reasons why it is best fitted for this work.
Next, a previously existing trust model for complex networks is described, including its advantages and reasons why it could be well-fitted for a vehicular environment, followed by a list of changes that must be made to the model in order for it to handle dynamic networks.
Finally, a schedule for the next steps of the project is shown.

\section{Social Networks and VANETs}
\label{section:socialvanets}
Some proposed trust models for vehicular networks, such as \cite{huang2014social}, state that the likelihood of two nodes meeting each other twice is too low to be relevant.
However, it stands to reason that, throughout the course of several days, many drivers take similar routes at similar times of day (e.g. to commute to work) and, therefore, their vehicles are in similar locations each day.
Additionally, many cities rely on main roads to serve as backbones to their traffic, meaning there is a high density of vehicles on those roads during rush hours.
Since that is true for a notable percentage of a city's fleet, it can also be assumed that those vehicles may frequently encounter each other during their commute.
While two vehicles that share a commute route may not be direct neighbors every day, they are likely to be relatively close to each other most days, meaning few hops separate them in the ad-hoc network.
Furthermore, certain pairs of vehicles are bound to be within communication range of each other nearly every day.
Examples of these include vehicles whose owners are neighbors or coworkers.
Such vehicles' trust relationship should become steady over time and, in the case of positive trust, they can use each other's information to learn more about other nodes in the network.

@@

Most cities also have one or more types of mass transit systems (buses or trains).
Those vehicles can also be part of a VANET and communicate with private cars.
Buses share the same roads as cars, but instead of having specific destinations, they travel a predefined route during the whole day, usually tied to a tight schedule.
Trains travel on rails, so their contact with cars is less frequent, but it can also happen on railroad crossings; they travel long distances in relatively short amount of time, which helps the dissemination of data in a VANET.
In the same way that cars have a high probability of meeting more than once during their commutes, it is also very likely that they meet the same buses and/or trains frequently.

In \cite{da2013effective}, \cite{cunha2014vehicular}, and \cite{cunha2014possible}, the authors attempt to find features usually attributed to social networks in vehicular networks.
By using a data set from Zurich, they show that some metrics, such as clustering coefficient and number of encounters, have peaks during the rush hours.
They note that, during rush hours, the diameter of the graph decreases to around 6 hops; additionally, the frequency of total encounters between pairs of nodes in the network increases during those hours.
Although the authors do not quantify the encounters between specific pairs of nodes, these numbers support the idea that daily commutes do indeed cause vehicular networks to exhibit social network features.

@@

@@

Most VANET trust models consider the Random Waypoint mobility model, i.e. each node has an origin point, chooses a random location, gets to that location, then chooses another random location and goes there, and so forth.
While this model is efficient for testing trust protocols, it doesn't truly represent vehicle mobility in the real world.

To make use of the properties described in \autoref{section:socialvanets}, it is important to choose a mobility pattern that properly represents the way vehicles move on a daily basis in the real world.
Therefore, the Working Day Movement Model \cite{ekman2008working} (WDM) is useful.
The model, developed for use in Delay-Tolerant Network (DTN) simulations, includes many of the features that are necessary to simulate the daily movement of a vehicular network.

As the name implies, the Working Day Model abstracts people's movement from their homes to their offices and back.
Each node has a home and a workplace and they need to travel back and forth between those locations on a daily basis.
Occasionally, nodes can also go to other locations for leisure.
As mentioned above, many drivers have routes they travel on daily, so the Working Day model is a more accurate representation, although it represents the mobility of humans instead of vehicle and requires some adjustments, which are listed later in this section.

The model proposed by the authors makes use of several other models for specific tasks.
The main mobility model defines nodes and gives them their destinations.
Within it, five other models are used:
\begin{enumerate}
\item 
The \textbf{home activity submodel} describes what nodes do at night, within their homes.
No movement is modeled.
Nodes can be relatives or neighbors, and therefore share the same home.
\item 
The \textbf{office activity submodel} describes the nodes' routines within their offices.
Nodes can go to other locations within the office (such as meeting rooms) and such movement is modeled.
Nodes with share the same office are coworkers.
\item 
The \textbf{evening activity submodel} is responsible for mobility outside the nodes' standard routine. 
They can meet at certain locations (such as restaurants) and spend a few hours gathered with friends.
\item
The \textbf{transport submodel} shows how nodes move around the city.
It includes another tier of submodels, responsible for modeling three different types of transportation: walking, driving, and riding a bus.
Nodes which own a car always use it, while the others can decide to walk or ride a bus depending on the distance between the origin and destination and the available bus stops.
The walking and driving submodels represent similar types of movement, although at different speeds, while the bus submodel follows cyclical routes and can take or deliver passengers at bus stops.
\item
The \textbf{map} represents the city in which the simulation runs.
Its streets constrain the movement of nodes and all homes and offices must be within the map boundaries.
The map can be divided into districts, which increases what the authors define as \textit{locality}.
In the simulation parameters, the number of nodes which reside and work within the same district can be chosen, which means those nodes rarely leave the district.
Nodes which reside and work in different districts serve to connect the network with their commutes.
\end{enumerate}

By thinking of these submodels for vehicles instead of people, it can become apparent how the frequency and length of encounters between nodes are similar in both instances.
If two vehicles belong to family members or neighbors, they likely spend most of the night within communication distance, while coworkers' cars spend the office hours close by.
Cars can also meet each other frequently if their drivers go out with friends.
In the vehicular case, there is the added layer of encounters: cars can communicate frequently with buses and other cars that take the same route daily, although the drivers are likely complete strangers.

In the original article, nodes are devices (such as smartphones) being carried by humans.
Therefore, the Working Day model represents not only people's movements inside their cars, but also within their offices, walking on foot, or riding a bus.
To adapt it to a VANET environment, changes need to be made to their definition of node, since they now represent vehicles instead of people. Some of those changes are as follows:
\begin{enumerate}
\item
The office activity submodel no longer needs to model movement within the office and can be identical to the home submodel.
In both, a node can move a small amount once after reaching the office or home, to simulate parking.
This can be done using the Working Day model's parameters.
\item
The walking submodel needs to be disabled, since all nodes are either cars or buses.
\item
The bus submodel needs to be changed so that each bus is one node in the network, which follows a predefined route with bus stops.
In the original model, each bus could carry several nodes, but this is no longer necessary.
\end{enumerate}
Other necessary changes might become apparent during the development of the study.

@@

The input graph $T = (V,O)$ is a static, connected, and directed graph containing all trust relationships in the network.
Such relationships are binary, so there are no varying degrees of trust: either one node trusts another completely (edge value is $1$), or it distrusts the other completely (edge value is $0$).
The relationships are also directed, meaning that if the value of $A\rightarrow B$ is $1$, $B\rightarrow A$ is not necessarily $1$.

The process for identifying malicious nodes within $T$ is as follows:

First, $T$ is separated into strongly components using Tarjan's algorithm \cite{tarjan1972depth}.
In each of these components, all nodes are connected by edges of value $1$.
In other words, within a single component, all nodes trust one another completely; nodes connected by edges of value $0$ are separated into different components.
Each of these components becomes a node of a component graph $T' = (V', O')$.

The creation of the graph $T'$ simplifies the remaining computation.
Since each node of $T'$ is a vertex $v' \in V'$ and each vertex $v'$ is a component of $T$ in which all nodes trust each other, for the purposes of identifying malicious nodes, all nodes within each of those components can be treated as one.
They can either be benign nodes which legitimately trust one another, or malicious nodes colluding with each other.
After the formation of $T'$, one or more heuristics can be used to classify the nodes as benign or malicious.

The article describes the coloring heuristic, which uses a graph coloring algorithm, either DSATUR \cite{brelaz1979new} or the algorithm proposed in \cite{mittal2011graph}.
Graph coloring is a classic problem of graph theory, in which the objective is to assign each node in a graph a color so that no two neighboring nodes share the same color.
After running either algorithms with graph $T'$, the color with the most nodes in $T'$ is classified as correct, and all others are classified as malicious.
Once this information in $T'$ is brought back to graph $T$, it is trivial to label the nodes in $T$ as either benign or malicious based on their components' classifications.

In the experiments shown in the article, the coloring heuristic shows promising results, identifying a high ratio of the malicious nodes in the network.
Other heuristics are experimented with, but were less effective in detecting malicious nodes, or provided too many false positives.
Therefore, for the purposes of this paper, only the coloring heuristic is considered.

Two types of experiments were made in each network: first, all malicious nodes inverted the edge weights leading to their neighbors; second, malicious nodes randomly inverted or not the weights.
In the first scenario, the results show excellent precision in most networks, detecting nearly every malicious node.
Experimenting with the second scenario, the results are less precise, however still promising: with up to 20\% of malicious nodes in the network, the error rate is under 7\%, while with the worst case, 50\% of the network being malicious, the error rate is approximately 15\%.

The authors suggest running the algorithm repeatedly after removing the malicious nodes from the network.
By doing this, nearly all malicious nodes are detected by it even when randomly changing edge weights.

%$G = (V,E)$: undirected topology graph, in which $V$ are the vertices and $E$ are the edges.
%
%$T = (V,O)$: directed trust graph, in which $O$ are the nodes' opinions about each other.
%
%$G_t,T_t$: snapshots of $G$ and $T$ in a timestamp $t$.
%
%$G_i,T_i$: local knowledge of $G$ and $T$ of a node $i$.
%
%$T' = (V',O')$: component graph of $T$.

\section{Necessary changes to the trust management scheme}
\label{section:changes}
While the algorithm described above works well for static graphs, some important modifications will have to be made to accommodate dynamic graphs.
The main changes planned are described below.

\subsection{Trust graph}
The original work's scope does not include the generation of the trust graph, as it is a parameter to the algorithm.
In dynamic graphs, trust relationships change over time, so how those changes affect the proposed trust model have to be considered.
This includes not only the full figure of the graph, but also each node's views on its neighbors.

\subsection{Strongly connected components}
Strongly connected components, or components in which all nodes have positive trust relationships with each other, are somewhat different in dynamic graphs.
As nodes enter, leave, or change locations in the network, the components change accordingly.
Therefore, our algorithm will have to work using ``snapshots'' of the graph, meaning each measurement will be valid for a specific timestamp.
Since the graph changes with time, for every timestamp $t$, there is a corresponding topology graph $G_t=(V_t, E_t)$, which includes the available vertices and edges in that moment in time, and a trust graph $T_t=(V_t, O_t)$, with the nodes' opinions at that moment.

In a later step, it might be useful to consider how specific nodes may change over several snapshots.
Specifically, the suggestion of running the algorithm in iterations, by removing the malicious nodes in each step, may be applied with the peculiarities of a dynamic network.

\subsection{Graph knowledge}
In the original paper, the malicious nodes are identified by a central entity with access to all nodes' trust values.
Not only does our work plan to decentralize this procedure, having complete knowledge of the graph is unfeasible in large-scale dynamic networks such as VANETs.
Therefore, our algorithm needs to work using only a partial understanding of the network.
For this to be viable, each node might have to gather information not only from its views on its neighbors, but also from its neighbors' views.

@@

Thus, each node has its own model of the network topology, $G_i$, and generates a trust graph $T_i=(V_i, O_i)$, in which $i$ is the node's identifier.
Combined with the necessity of timestamps explained above, this results in a graph $T_{it}=(V_{it}, O_{it})$ for each node and each timestamp, which is the input of the new algorithm.
Accordingly, there are also component graphs $T'_{it}=(V'_{it}, O'_{it})$, generated on each instance of the algorithm.

@@

Since nodes interact with each other occasionally and might learn information from other nodes, a range of $[0,1]$ is useful to express how one trust value can change over time.
As one node learns more about another, the value can grow or diminish and, once it goes above or below a certain threshold, the neighboring node can be deemed trustworthy or not.
The rate in which trust increases or decreases must be experimented with; it could be useful to have trust decrease faster than it increases, but that might also cause false positives in the case of occasional mistakes.

\subsection{Datasets}
The datasets used for experimentation must be changed accordingly.
Instead of using data gathered from social networks, which are static, dynamic network datasets must be used, such as traffic information for cities.

At first, the objective is to test using the Working Day Movement Model, setting parameters that contribute to the validation of the algorithm.
When the simulation begins, a set number of nodes are malicious and, therefore, other nodes will have low trust in them after interacting.
In time, benign and malicious nodes can change their behavior and, accordingly, their trustworthiness will be updated.

@@

\begin{enumerate}
	\item \textbf{Changes to the malicious node identification algorithm}. Develop and adapt the algorithm using the changes listed in \autoref{section:changes}.
	\item \textbf{Changes to the movement model}. Develop and adapt the Working Day Movement Model according to \autoref{section:workingday}.
	\item \textbf{Study of the simulator}. Several simulators for vehicular networks exist, and one must be chosen in order to run simulations using the newly developed model. The Working Day Movement Model was tested with the ONE Simulator \cite{keranen2009one}. The source code for both the simulator and the WDM generation can be found online \cite{onerepo}, and will be used for the necessary simulations. 
	\item \textbf{Simulations and adjustments}. Once the core of the project has been developed and a simulation has been chosen, simulations begin. The models may be tweaked in order to achieve better results, and all data from the process will be collected.
	\item \textbf{Analysis of data and results}. With the data collected from simulations, it will be possible to observe the outcome of the proposed trust model. If tweaks were made to the model during simulations, those changes can be listed, showing which ones provided better results.
	\item \textbf{Writing and submission of article}. Having concluded development, an article will be written explaining the motivations, challenges and results of the study. This article will be submitted to a congress.
	\item \textbf{Writing of dissertation}. Finally, the whole process will be detailed within the dissertation.
\end{enumerate}

\begin{table}[h!]
\centering
\begin{tabular}{ |p{0.7cm}||p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}|p{0.7cm}| }
 \hline
 \textbf{Task} & May & Jun & Jul & Aug & Sep & Oct & Nov & Dec & Jan & Feb & Mar\\
 \hline
 \hline
 \textbf{1} & \checkmark & \checkmark & \checkmark & & & & & & & &\\
 \hline
 \textbf{2} & & \checkmark & \checkmark & \checkmark & & & & & & &\\
 \hline
 \textbf{3} & \checkmark & \checkmark & \checkmark & \checkmark & & & & & & &\\
 \hline
 \textbf{4} & & & & \checkmark & \checkmark & \checkmark & \checkmark & & & &\\
 \hline
 \textbf{5} & & & & & & & \checkmark & \checkmark & \checkmark & &\\
 \hline
 \textbf{6} &  &  & & & & & & \checkmark & \checkmark & &\\
 \hline
 \textbf{7} &  &  & & & & & & \checkmark & \checkmark & \checkmark & \checkmark \\
 \hline
\end{tabular}
\caption{Expected schedule}
\label{table:schedule}
\end{table}

@@
